---
#YAML Header
title: "Lab 1"
author: "zewahyu"
date: ""
output: html_document
---

##### R Markdown Cheatsheet:
[Cheatsheet URL](https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)

### 1. Changing the author field and file name.

* (a) Change the `author:` field on the Rmd document to your own name + Studend ID.

* (b) Rename this file to "lab01_SID.Rmd", where SID is changed to your own Student ID.

### 2. Markdown

# Task1

Refers to the Markdown Cheatsheet, create a small table with 2 columns: "Course Code" and "Course Title".
And 2 rows:
"ISOM3360" - "Data Mining for Business Analytics"
"ISOM3210" -  "Information Systems Analysis and Design"

The course codes are in italics.

## Answer for Task1
Course Code | Course Title
------------|------------
*ISOM3360* | Data Mining for Business Analytics
*ISOM3210* | Information Systems Analysis and Design



## End of Task1


### 3. Assigning Variables
Create and assign values "A", "b", 3 to variable a, b, c with 3 different assignment operators respectively.

# Task2
```{r Task2}
(a = "A")
(b <- "b")
(3 -> c)
```


### 4.  Creating sequences
We just learned about the `c()` operator, which forms a vector from its arguments.  If we're trying to build a vector containing a sequence of numbers, there are several useful functions at our disposal.  These are the colon operator `:` and the sequence function `seq()`.

##### `:` Colon operator: 
```{r colon operator}
1:10 # Numbers 1 to 10
127:132 # Numbers 127 to 132
1000:1 # Numbers 1000 to 1
```

##### `seq` function: `seq(from, to, by)`
```{r seq function}
seq(1,10,1) # Numbers 1 to 10
seq(1,10,2) # Odd numbers from 1 to 10
seq(2,10,2) # Even numbers from 2 to 10
```

```{r example}
(x <- c(11, 12, 13, 14, 15, 16))
(x1 <- 11:16)
(length(x)) # number of elements in x
(length(x1))
```
Question yourself: 
What is the difference between x and x1?

Can we get the same result as seq(2,10,2) by using colon?



### 5. Indexing of Vectors (Positive, Negative) 
From part 4: we can select part of the elements in the vector 'x' with a vector of index using '[]'. e.g.:
```{r vector index}
x[2:4]
x[c(2,4,6)]
x[-4:-5] # expect 4 to 5; negative means NOT select
x[6:1]
```

### 6 Names of Vectors 

``` {r vector name}
attributes(x)
names(x)
```

```{r}
names(x) = c("one", "two", "three", "four")
names(x)
attributes(x)
```
```{r}

names(x) = c("one", "two", "three", "four", "one", "two")
names(x)
names(x[6])

```
What if there are two elemet with the same name?
```{r}
x["one"]
```


### 7. Vectorized Characteristics

x = c(1, 2, 3, 4, 5)
y = c(5, 4, 3, 2, 1)
x + y => c( 1 + 5, 2 + 4, 3 + 3, 4 + 2, 5 + 1)

what if the length of two vector are not the same?
```{r}
a<- 1:5
b<- 3:5
a+b
```



Task3: 
Create two variable a and b, assign value 1 to a, 100 to b.
Create a vector contain numbers from a to b, name the vector 'k'. Calculate k plus the reverse order of k.

Restrictions:
- You are not allow to use the function `rev()`.
- Please use a way that related to indexing.

Tips: For indexing, index 1 always means the first element, but we do not have a number to represent the last number. In this task, you are not allow to use the index 100 to represent the last item. When grading your task, I will use other number instead of 1 and 100 e.g. 30 and 55.

i.e.
k + reverse k:
1 + 100
2 + 99
3 + 98
...
...
99 + 2
100 + 1

Output: (length of the output is 100)
101
101
...
...
101

p.s DO NOT calculate manually. This is a programming course. 

``` {r}
# example answer for using rev():
a<-1
b<-100
k<- a:b
k + rev(k)
```

# Task 3
```{r Task3}
# Your code here
a<-1
b<-100
k<- a:b
k+(b:a)
```


## Submission:
When you finish the 3 tasks, click the "Knit" button to generate the html document. Submit the html file as your lab submission.

!!! Remember to edit the 'author' information in YAML Header of this Rmd file. If I see "Josh Man" there, I may consider that this is NOT your work. :)


