---
title: "Practicing Advanced Looping and the Split-Apply-Combine Manipulation"
author: "zewahyu"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy=TRUE, eval = FALSE)
```

### Part 1: Function

##Task 1.1

In part 1, we will try to practice more on function.
Write a function isLeapYear with a parameter named year.
The parameter needs to be greater than or equal to 1 and less than or equal to 9999.
If the parameter is not in that range return false. 
Otherwise, if it is in the valid range, calculate if the year is a leap year and return true if it is, otherwise return false. 
A year is a leap year if it is divisible by 4 but not by 100, or it is divisible by 400.
Examples of input/output:

* isLeapYear(-1600); →  should return false since the parameter is not in the range (1-9999)

* isLeapYear(1600); → should return true since 1600 is a leap year

* isLeapYear(2017); → should return false since 2017 is not a leap year

* isLeapYear(2000); → should return true because 2000 is a leap year 

```{r task1.1}
#Write your code here
isLeapYear <- function(year) {
  if(year>=1 & year<=9999){
    if( (year%%4==0 & year%%100!=0)|(year%%400==0) ){
      return(TRUE)
    }  
  }
  return(FALSE)
}
isLeapYear(2020)


```

## Task 1.2

1) Create Variable Daysnum and assign value 0 to it

2) Write another function getDaysInMonth with two parameters month and year.

3) create variable result inside the fuction and assign value 0 to it

3) 
If parameter month is < 1 or > 12 result= FALSE.
If parameter year is < 1 or > 9999 then result= FALSE.
This function needs to assign the number of days in the month to result. Be careful about leap years they have 29 days in month 2 (February).
You should check if the year is a leap year using the function isLeapYear described above.
Examples of input/output:

* getDaysInMonth(1, 2020); → result= 31 since January has 31 days.

* getDaysInMonth(2, 2020); → result= 29 since February has 29 days in a leap year and 2020 is a leap year.

* getDaysInMonth(2, 2018); → result= 28 since February has 28 days if it's not a leap year and 2018 is not a leap year.

* getDaysInMonth(-1, 2020); → result= FALSE since the parameter month is invalid.

* getDaysInMonth(1, -2020); → result= FALSE since the parameter year is outside the range of 1 to 9999.

You may use switch and if to finish this part
4) Assign the result to Daysnum

```{r task1.2}
# Write your code here
Daysnum <- 0
getDaysInMonth <- function(month,year){
  result <- 0
  if(month<1 | month>12 | year<1 | year>9999){
    result <- FALSE
  }
  else{
    result <- switch(as.character(month), "1"=,"3"=,"5"=,"7"=,"8"=,"10"=,"12"=31,
                                          "4"=,"6"=,"9"=,"11"=30,
                                          "2"={
                                            if(isLeapYear(year)) 29
                                            else 28
                                          })
  }
  Daysnum <<- result
}
getDaysInMonth(2,2019)
Daysnum
```

### Part 2: Calculating the Ratio of the Government's Debt to the GDP

Gross domestic product (GDP) is a measure of the total market value of all goods and services produced in a given country in a given year.

An important claim in economics is that the rate of GDP growth is closely related to the level of government debt, specifically with the ratio of the government's debt to the GDP.  The file `debt.csv` on Canvas contains measurements of GDP growth and of the debt-to-GDP ratio for twenty countries around the world, from the 1940s to 2010.  Note that not every country has data for the same years, and some years in the middle of the period are missing data for some countries but not others.

Load the data into a dtaframe called `debt`.  

```{r}
debt<-read.table("debt.csv",sep = ",", header = T)
head(debt)
```

We should have 1171 rows and 4 columns. And there are no missing values in all columns.

```{r}
dim(debt)
lapply(debt, function (x) length(x[is.na(x)]))

```

2.1 Use `split` and `sapply` to calculate the average GDP growth rate for each country (averaging over years).  (The average growth rates for Australia and the Netherlands should be $3.72$ and $3.03$.)  Present a table of the twenty growth rates.

```{r task2.1, echo=TRUE}
#Write your code here
#Growth <- split(debt,debt$Country)
#sapply(Growth, function(x) mean(x$growth))
Growth <- split(debt$growth, debt$Country)
sapply(Growth, mean)
```
